Exploiting the Social Graph: Increasing Engagement via Collaborative Interactive Evolution

### 2017-01-27 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Conclusions revised
And cut back using dark arts to 8 pages again. Spell-check and
submit and on to the next paper :-)
Great job, @mariosky!

Is important to notice that this model is still a partial view of the IEC system,
and other models can could be used in practice when implementing the
system. % It is also a bipartite graph, which could be converted to a
% single-party graph with only one type of node. 
% I don't get this comment, yes some relations are bipartite, but If we see the whole
% graph I think is a multi-graph.   - Mario 
% I will check the  single-party graph conversion you suggest, I don't
% know the concept. - Mario
% Does not matter much... it converts a bipartite graph to another
% graph with a single kind of nodes, phenotypes or users, for instance
% - JJ

% I don't think "collections" should be nodes too. They are simply
% attributes for an individual - JJ
% They are nodes, I added the reason above. - Mario
For instance a relational database was used for the implementation of a 
basic user profile and authentication module. Also the active population 
was kept in a key-value store in memory for performance reasons.  
Nevertheless, having a multi-model implementation can give important 
insights of the behavior of the system. This architecture was validated
by a case study, requiring the interaction of all of the components.

@@

Collaborative and volunteer based IEC systems involve the dynamic 
interaction of many entities and artifacts. Employing a multi-model approach
can benefit researchers to understand and visualize this kind of systems better.
In this paper a graph model was proposed as a complement to current models to
improve the visualization of different experiments. Further more, the same graph enabled
the implementation of a gamification technique to improve engagement in
a case stady.

One of the interesting future lines of work would be to look a bit
more closely at the behavior of users rating the system. These initial
experiments hint at a possible power law, which might indicate that
the IEC system could be self-organizing, a process that would allow it
to reach a critical state, as has been found in software repositories,
for instance \cite{Merelo2016:repomining}. The dynamics of this kind
of system are fundamentally different, and our future research will
include exploring these aspects of the system.

Another line of work would be to study the negative effects of using 
gamification techniques to improve engagment, like cheating or competition.
Finally, the refinement of the proposed Human-Centered frameworkwill need
more case studies and further multi-disciplinary research.

\section*{Acknowledgment}
Space reserved for Acknowledgment text, Lorem ipsum dolor sit amet, consectetur adipiscing elit,
sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis 
nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.

>>>>

Is important to notice that this model is still a partial view of the IEC system,
and other models can could be used in practice when implementing the
system. % It is also a bipartite graph, which could be converted to a
% single-party graph with only one type of node. 
% I don't get this comment, yes some relations are bipartite, but If we see the whole
% graph I think is a multi-graph.   - Mario 
% I will check the  single-party graph conversion you suggest, I don't
% know the concept. - Mario
% Does not matter much... it converts a bipartite graph to another
% graph with a single kind of nodes, phenotypes or users, for instance
% - JJ
%
% I don't think "collections" should be nodes too. They are simply
% attributes for an individual - JJ
% They are nodes, I added the reason above. - Mario
For instance a relational database was used for the implementation of a 
basic user profile and authentication module. Also the active population 
was kept in a key-value store in memory for performance reasons.  
Nevertheless, having a multi-model implementation can give important 
insights of the behavior of the system. This architecture was validated
by a case study, requiring the interaction of all of the components.

@@

Collaborative and volunteer based IEC systems involve the dynamic 
interaction of many entities and artifacts. Employing a multi-model approach
can benefit researchers to understand and visualize this kind of systems better.
In this paper a graph model was proposed as a complement to current
models, initially to improve the visualization of different
experiments, but in this paper we prove that this model  enables
the implementation of a gamification technique to improve engagement in
a case study. Providing a common arena where users are aware of the
activities of other users in the social vicinity, as well as using
this graph to assign fitness allows in one hand for a greater
engagement by the users and from the algorithmic point of view a more
complex way of assigning fitness and push the generation of content
forward.

One of the interesting future lines of work would be to look a bit
more closely at the behavior of users rating the system. These initial
experiments hint at a possible power law, which might indicate that
the IEC system could be self-organizing, a process that would allow it
to reach a critical state, as has been found in software repositories,
for instance \cite{Merelo2016:repomining}. The dynamics of this kind
of system are fundamentally different, and our future research will
include exploring these aspects of the system. Another line of work would be to study the negative effects of using 
gamification techniques to improve engagement, like cheating or competition.
Finally, the refinement of the proposed Human-Centered frameworkwill need
more case studies and further multi-disciplinary research.

\section*{Acknowledgment}
Space reserved for Acknowledgment text, Lorem ipsum dolor sit amet, consectetur adipiscing elit,
sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis 
nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
